Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-08-25 ltx/data_paper/DataPaper.tex
edits to discussion

\subsection{Correlation Analysis}
The correlation analysis specifies an approximation for the support of both the disturbance covariance function and the connectivity kernel. Although the unknown parameters $\xi$ and $\sigma_{\varepsilon}^2$ can be set as described in \S\ref{subsec:CorrAnal}, the chosen values influence the exact shape of the kernel significantly. The analysis also assumes the sigmoidal firing rate in the active region and as a result  the kernel and disturbance amplitudes cannot be inferred only through the correlation analysis. This step might be considered as a prerequisite for the EM algorithm described in \S\ref{sec:EstimationAlgorithm} where the approximated supports are used to estimate the gain of the kernel and the field disturbance variance. Knowing the spatial extent of the connectivity kernel greatly improves the speed of the estimation algorithm as the number of basis functions for the kernel decomposition is significantly reduced  compared to the case where the basis functions are arranged across the entire spatial domain. This also improves the uncertainty of the estimates as a lower number of unknown parameters need to be estimated. The approximated support of the disturbance covariance function facilitates the application of the EM algorithm. This way the disturbance covariance matrix can be decomposed into two parts: an unknown scalar and a constant matrix depending only on the inferred spatial support. Therefore, the estimation problem of the disturbance covariance matrix breaks down to the estimation of a single scalar parameter, improving the accuracy and the convergence property of the algorithm.

>>>>

\subsection{Correlation Analysis}
The correlation analysis specifies an approximation for the support of both the disturbance covariance function and the connectivity kernel. Although the unknown parameters $\xi$ and $\sigma_{\varepsilon}^2$ can be set as described in \S\ref{subsec:CorrAnal}, the chosen values influence the exact shape of the kernel significantly.

The derivation for the closed-form solution of the kernel requires linearisation of the sigmoidal activation function about the firing threshold. Therefore, the resulting kernel estimate is simply used as a guide to constrain the placement of basis function and the corresponding coefficients must still be inferred using the EM algorithm for an accurate representation of the connectivity structure. In fact, the correlation analysis can be considered a prerequisite for the EM algorithm described in \S\ref{sec:EstimationAlgorithm}, where the approximated supports are used to estimate the gain of the kernel and the field disturbance variance.

An alternative to estimating the support of the connectivity kernel is to place a regular grid of connectivity kernel basis function over the entire spatial domain of the field. However, the estimate of the spatial extent of the connectivity kernel greatly improves the speed of the estimation algorithm as the number of basis functions for the kernel decomposition can be significantly reduced. This also improves the uncertainty in the estimated coefficients, as a lower number of unknown parameters are estimated. The approximated support of the disturbance covariance function facilitates the application of the EM algorithm. This way the disturbance covariance matrix can be decomposed into two parts: an unknown scalar and a constant matrix depending only on the inferred spatial support. Therefore, the estimation problem of the disturbance covariance matrix breaks down to the estimation of a single scalar parameter, improving the accuracy and the convergence property of the algorithm.
